Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-05-14 paper/paper.tex
write on the constant T

Our 
When considering the commonly used duration of $25~\mathrm{ms}$, the performance drops down to $\textbf{90.9\%} \pm 4$. This demonstrates that the joint scattering is able to benefit from a larger time support, possibly to capture longer-term modulations which play an important part when considering extended playing techniques \cite{lostanlen2018extended}.

>>>>

Our best performing system operates with joint time--frequency scattering coefficients as spectrotemporal modulation features.
These features are extracted within a temporal context of duration equal to $T=\SI{1000}{\milli\second}$.
This value is considerably larger than the frame size of purely spectral features, such as spectral centroid, spectral flux, or mel-frequency cepstral coefficients (MFCC).

When considering the commonly used duration of $25~\mathrm{ms}$, the performance drops down to $\textbf{90.9\%} \pm 4$. This demonstrates that the joint scattering is able to benefit from a larger time support, possibly to capture longer-term modulations which play an important part when considering extended playing techniques \cite{lostanlen2018extended}.
